%-------------------------
% Resume in Latex
% Author : Andrei Tuta
% License : MIT
%------------------------

\documentclass[onesided,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}\usepackage{hyphenat}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------

{\small\begin{tabular}[c]{l}
  \textbf{Manchester,UK}\\
  \href{http://www.github.com/andreituta}{github.com/andreituta}\\
  \href{http://www.linkedin.com/in/andreituta}{linkedin.com/in/andreituta}
\end{tabular}}\hfill%
{\Large\bfseries\begin{tabular}[c]{c}
  Andrei Nicolae Tuță
\end{tabular}}\hfill%
{\small\begin{tabular}[c]{r}
  074 93935418  \\
  \href{mailto:tuta.andrei96@gmail.com}{tuta.andrei96@gmail.com}
  \\ \today
\end{tabular}}%


%-----------CAREER-----------------
\section{Professional Profile}
        
          { \quad \quad  Versatile and competitive professional with development experience ranging in size from small private projects to full scale applications, currently working on improving and expanding an online and mobile software e-commerce product. Driven by a passion for improving current understanding of technologies, expanding knowledge further and a desire for my team to succeed. }



%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
    \item{
     {\textbf{Programming Languages}}{:  Java, Javascript, SQL, Bash, Python, Haskell}}
     \item{
     {\textbf{Technologies and frameworks}}{: AWS, EC2, S3, Springboot, Docker, Git, , Node, MySQL, MongoDB, Eclipse, JUnit, Mockito }
    }
    \item{
    {\textbf{Spoken Languages}}{: Romanian, English, French, Spanish}    
    }
 \resumeSubHeadingListEnd
 
%-----------EXPERIENCE-----------------
\section{Professional History}
  \resumeSubHeadingListStart
  
  \resumeSubheading
    {Aeroparker}{Stockport, UK}
    {Java Developer}{Oct 2018 - present}
      \resumeItemListStart
        \resumeItem{Spring expertise}
            {Developed implementations of Spring based applications based on REST, Jooq, JWT and other tools. }
        \resumeItem{BI tool}
            { Developed a BI tool used daily by a large number of clients to get yearly, monthly and hourly occupancy through REST calls and using D3.js visualisation.}
        \resumeItem{Java EE}
            { Worked on developing new features for the Java core project, built using Apache Tomcat, AJAX technologies and JSP.}
          
      \resumeItemListEnd
      
%   \resumeSubheading
%     {URJ 6 Points Sci-tech}{Byfield, MA}
%     {Counselor/ Specialist}{Jun - Aug 2018}
%       \resumeItemListStart
%         \resumeItem{Programming assistant}
%           {Helped instructors deliver the programming workshop, focused on teaching elementary Java, and Processing}
%         \resumeItem{Workshop Instructor}
%           {Volunteered to run my own workshop, teaching participants basic HTML, CSS, JS for coding a virtual board game.}
%       \resumeItemListEnd
    
    \resumeSubheading
    {Birmingham City University}{Birmingham, UK}
    {Technical Student Assistant}{Sep 2017 - Jun 2018}
      \resumeItemListStart
        \resumeItem{Student Assistant \& Ambassador}
          {Managed and aid groups of students during courses and activities. Tasks varied explaining programming concepts and active development to large scale organisation of an event and providing tech support if needed. }
        \resumeItem{Innovation Fest Mentor}
          {Supervised two teams of students with the technical development, planning and pitching of their entries for a local technology contest, which they won. }
      \resumeItemListEnd

    \resumeSubheading
    {Oracle Romania}{Bucharest, RO}
    {Junior Database Administrator}{Jun - Sep 2017}
      \resumeItemListStart
        \resumeItem{Oracle DBA training}
          {Received training covering topics such as administration, back-up, recovery and automation.}
        \resumeItem{MySQL}
          {Participated in guided training on MySQL and Orace SQL}
      \resumeItemListEnd
      
    
    % \resumeSubheading
    % {The Business Information Portal}{Birmingham,UK}{Software Developer}{Oct 2015 - Sep 2016}
    %     \resumeItemListStart
    %         \resumeItem
    %           {Part-time development}
    %           {Worked within a small team to develop solutions for people with visual impairment. Gained experience working within a large code base and improved at writing clean, testable  code.}
    %          \resumeItem
    %          {Testing}
    %          {Applied Agile methodologies and CI processes with Test Driven software development in various environments.Learned the importance of risk management in software: continuous builds, Quality Assurance and release cycles .}
    %     \resumeItemListEnd
      
      \resumeSubheading
    {Logika IT Solutions}{Bucharest, RO}
    {Junior Database Administrator }{Jun - Aug 2016}
      \resumeItemListStart
        \resumeItem{Summer internship}
        {Worked as a trainee in a team of 4 people managing databases for multiple clients. Other responsibilities included writing reports and suggestions on ways to improve the work-flow and diminish cost. }
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
  {Birmingham City University}{Birmingham, UK}
  {Data Analysis, Software Engineering 
  \& Database administration}
  {2015 - 2018}
    \resumeSubheading
  {Universidad de Alcala}{Alcala de Henares, SP}
  {Software Design, Cloud computing \& Agile Development }
  {Jan - Jun 2017}
    
  \resumeSubHeadingListEnd



% % ------------Extracurricular activities------------
 \section{Extracurricular activities}
    \resumeSubHeadingListStart
        \resumeSubheading
        {Volunteer} {CodeUp Stockport}
        {Volunteering with helping our members at our monthly Meetups.}{Jul 2019 - present}
        \resumeSubheading
        {Writer}{Medium}
        {Writing articles featuring subjects related to programming \& literature.}
        {2017 - present}
          \resumeSubheading
        {Camp counselor}{URJ 6Points Sci tech}
        {Assisted and organised programming workshops on Java, \& Processing}
        {Jun - Aug 2018}
        \resumeSubheading
        {Outward Mobility Ambassador} {BCU CEBE}
        {Managing and recruiting students for international programs \& social media development.} {Jan - Jun 2018}
        \resumeSubheading
        {President}
        {BCU RoSoc}
        {Event planning, budgeting \& team management.}{2016 - 2018}
        \resumeSubheading
        {Secretary}
        {Rotaract Club Birmingham}
        {Event planning, PR \& note-taking.}{2015 - 2017}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
